% === HOMEWORK PORTION ===
\documentclass[answers]{exam}

\input{preamble.tex}
\input{macros.tex}

\renewcommand{\questionlabel}{\textbf{Problem \thequestion.}}
\renewcommand{\solutiontitle}{}

\title{\Huge{Midterm Problem 8 Redo}
	\\
\Large\scshape{Graph Theory and Combinatorics}}
\author{Nawat Ngerncham (6380496)}
\date{\today}

\begin{document}

\maketitle

\begin{questions}
  \setcounter{question}{7}
  \question Prove that a graph \(G\) is 2-connected if and only if
  for every ordered triple \((x, y, z)\) of vertices, there is an
  \(x-z\) path through \(y\).
  \begin{solution}
    First, we will show the forward direction: If a graph is
    2-connected, then for every ordered triple \((x, y, z)\) of
    vertices, there is an \(x-z\) path through \(y\). Fix \(x,
    z\) to be distinct vertices in \(G\). Without loss of
    generality, there must be \(x-y\) and \(x-z\) paths since the
    graph is connected. Now, consider \(y\). If \(y, z\) are
    adjacent, then we are done and we have a \(x-z\) path that
    goes through \(y\).

    Otherwise, there are at least 2 internally disjoint \(y-z\)
    paths since the graph is 2-connected by Menger's Theorem.
    Then, there is a \(y-z\) path that does not go through \(x\)
    by the Pigeonhole Principle. Let us call this path \(P\).
    Hence, there is a \(x-z\) path that goes through \(y\) by
    concatenating the original \(x-y\) path and \(P\). Therefore,
    if a graph \(G\) is 2-connected, then for every ordered
    triple \(x, y, z\) in \(G\), there is an \(x-z\) path through
    \(y\).

    Next, we will show the converse direction: If for every
    ordered triple \(x, y, z\) of vertices, there is an \(x-z\)
    path through \(y\) in a graph \(G\), then \(G\) is
    2-connected. We will show this by contrapositivity:
    Assume that \(G\) is not 2-connected (i.e., \(G\) is 
    1-connected). Then, we will show there are \(x, y, z \in 
    V(G)\) such that that there is no \(x-z\) path
    through \(y\) in a graph \(G\).

    Since \(G\) is 1-connected, there is a cut vertex. Fix \(z\)
    to be a cut vertex and let \(x\) and \(y\) belong to 
    different components in \(G-z\). Note that \(G-z\) must have
    two components. Otherwise, \(G-z\) would still be connected
    and \(z\) would not be a cut vertex. Consequently, there
    would be no \(x-z\) path through \(y\).
  \end{solution}
\end{questions}

% % in case of needing citations
% \bibliographystyle{plainurl}
% \bibliography{refs}

\end{document}
